Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-20 paper.tex
Replaced screenshots
Replaced results in charts

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot-2.png}
\caption{Screenshot of Boolean AND.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot-2.png}
\caption{Screenshot of Boolean XOR.}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=2.2 GHz i7 with AMD Radeon HD 6750M,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\label{macbook-performance-chart}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.33 GHz Intel Core i7 with Quadro FX 5800,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 51)
  (200, 28)
  (300, 19)
  (400, 14)
  (500, 11)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 76)
  (200, 39)
  (300, 27)
  (400, 23)
  (500, 17)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 130)
  (200, 68)
  (300, 46)
  (400, 36)
  (500, 29)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 172)
  (200, 89)
  (300, 60)
  (400, 46)
  (500, 38)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Core i7 system with a Quadro FX 5800 video card.  Here the difference between
the methods is more dramatic.  Both slicing methods handedly beat the
Boolean-based methods.
}
\label{workstation-performance-chart}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot.png}
\caption{Screenshot of Boolean AND.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot.png}
\caption{Screenshot of Boolean XOR.}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=2.2 GHz Intel Core i7 with AMD Radeon HD 6750M,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 12)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 12)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Depth-Masking}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{General Slicing}
\addplot coordinates {
  (100, 12)
  (200, 6)
  (300, 4)
  (400, 3)
  (500, 2)
};
\addlegendentry{Optimized Slicing}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Core i7 system with an AMD Radeon HD 6750M video card.
}
\label{macbook-performance-chart}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.33 GHz Intel Core i7 with Quadro FX 5800,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 38)
  (200, 24)
  (300, 18)
  (400, 14)
  (500, 12)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 37)
  (200, 25)
  (300, 18)
  (400, 15)
  (500, 12)
};
\addlegendentry{Depth-Masking}
\addplot coordinates {
  (100, 32)
  (200, 17)
  (300, 11)
  (400, 9)
  (500, 7)
};
\addlegendentry{General Slicing}
\addplot coordinates {
  (100, 35)
  (200, 18)
  (300, 12)
  (400, 9)
  (500, 7)
};
\addlegendentry{Optimized Slicing}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Core i7 system with a Quadro FX 5800 video card.
}
\label{workstation-performance-chart}
\end{figure}
